\large{McGill University | Desautels Faculty of Management}\\ \hfill \break \hfill \break \hfill \break \hfill \break \\\Large MGSC 670 - Revenue Management\\ \textbf{Group Assignment 1: Markdown Strategy}\\ \hfill \break \hfill \break

### 2023-05-16 manuscript/manuscript.tex
updated

\pagenumbering{arabic}
\setcounter{page}{1}
\section{Introduction}
Any modern consumer recognizes words like “discount”, “clearance”, or “liquidation.” 
Behind the scenes of these words is a carefully orchestrated pricing and markdown strategy for each product from retailers. 
The relationship between price and demand is well documented and pricted by the field of economics. 
With perfect information and competition, as the price increases, the demand decreases, and vice-versa. 
Simplified price is, therefore, a control mechanism for the quantity of an item sold.

@@

We expect this model to have a lower difference consistency than the short-term naïve average, since it is likely that more of the units sold will reach different price points faster than the average model price evolution. 
However, we also expect this model to have the highest average revenue of all models.

>>>>

\pagenumbering{arabic}
\setcounter{page}{1}
\section{Introduction}
Any modern consumer recognizes words like “discount”, “clearance”, or “liquidation.” 
Behind the scenes of these words is a carefully orchestrated pricing and markdown strategy for each product from retailers. 
The relationship between price and demand is well documented by the field of economics. 
With perfect information and competition, as the price increases, the demand decreases, and vice-versa. 
Simplified price is, therefore, a control mechanism for the quantity of an item sold.

@@

We expect this model to have a lower difference consistency than the short-term naïve average, since it is likely that more of the units sold will reach different price points faster than the short-term average model. 
However, we also expect this model to have the highest average revenue of all models.
